SST_patterns

### 2020-01-26 SST_patterns.Rmd
graphs

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product)) +
  facet_wrap(~site)

>>>>

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product),  
                       position="identity", alpha=0.6) +
  facet_wrap(~site) +
theme_bw()

ggplot(CMC_dur, aes(duration, colour = product)) +
  geom_freqpoly() +
  facet_wrap(~site) +
  theme_bw()
```
